Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-03-08 Methods-and-Results.Rmd
joint forest plot function added

      meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
      meta.parametric.sum$CI.Student[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),", ",round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),"]",sep="")
      meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")

@@

    eff <- escalc(data = lmMetaTbl, 
                  slab = coef,
                  measure = "SPCOR",
                  ti = tval,
                  ni = n,
                  mi = m,
                  r2i = Rsq)
    meta <- rma(yi = yi,
                vi = vi, 
                data = eff, 
                method = "FE", # "REML", 
                slab = paste(coef, sample, sep=" - "))

    k <- length(var) * length(studies)
    png(file = "Figures/forestParametricGeneralLm.png", height = 200 + 40*k^.85) 
      metafor::forest(meta, xlim=c(-2, 2), cex=0.75, ylim=c(-1, 20), rows=c(22:20,16:14,10:8,4:2), 
                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)+1),
                      mlab="", main=paste0("Meta Analysis: Forest Plot [Parametric] \n(",name,")")) # , xlab = "Standardized Beta"
      par(font=2)
      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
      m=1
      for(i in 3:1){
        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
        m <- m+6
      }
      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
      text(2, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
    dev.off()

@@

    meta.parametric.plt.widedata <- data.table::melt.data.table(
      data = meta.parametric.plt.data,
      id.vars = c("effect", "name"),
      measure.vars = patterns(
        beta = "beta",
        lwr = "lwr",
        upr = "upr",
        CI = "CI",
        pval = "pval",
        star = "star"
      ),
      variable = "sample" # sample info missing
    )

@@

# Alternative Meta:
      Metaan::estmeta(
        Beta = GeneralLmerMetaTbl$B[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
        l = GeneralLmerMetaTbl$lwr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
        u = GeneralLmerMetaTbl$upr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
        test = "FIXED", # "RANDOM"
      )
```

@@

@@

>>>>

      meta.parametric.sum$CI.Worker[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2)),"]",sep="")
      meta.parametric.sum$CI.Student[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2)),"]",sep="")
      meta.parametric.sum$CI.Medical[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2)),"]",sep="")

@@

    eff <- escalc(data = lmMetaTbl, 
                  slab = coef,
                  measure = "SPCOR",
                  ti = tval,
                  ni = n,
                  mi = m,
                  r2i = Rsq)  %>%
    mutate(effLwr = yi - 1.96 * sqrt(vi),
           effUpr = yi + 1.96 * sqrt(vi),
           effCI = paste("[", format(round(effLwr, 2), nsmall = 2), ", ", format(round(effUpr, 2), nsmall = 2), "]", sep = ""),
           name = strLabFix(coef),
           study = strStudyFix(sample))

    meta <- rma(yi = yi,
                vi = vi, 
                data = eff, 
                method = "FE", # "REML", 
                slab = paste(coef, sample, sep=" - "))

    k <- length(var) * length(studies)
    png(file = "Figures/forestParametricGeneralLmOld.png", height = 200 + 40*k^.85) 
      metafor::forest(meta, xlim=c(-2, 2), cex=0.75, ylim=c(-1, 20), rows=c(22:20,16:14,10:8,4:2), 
                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)+1),
                      mlab="", main=paste0("Meta Analysis: Forest Plot [Parametric] \n(",name,")")) # , xlab = "Standardized Beta"
      par(font=2)
      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
      m=1
      for(i in 3:1){
        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
        m <- m+6
      }
      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
      text(2, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
    dev.off()

@@

  library(splitstackshape)
    meta.parametric.plt.longdata <-
      merged.stack(
        meta.parametric.plt.data,
        var.stubs = c("beta", "lwr", "upr", "CI", "pval", "star"),
        sep = "."
      ) %>%
      rename(sample = .time_1) %>%
      mutate(sample = gsub('Worker', 'Study 1',
                      gsub('Student', 'Study 2',
                      gsub('Medical', 'Study 3', sample)
                           ))) %>%
    arrange(match(effect, c("SumContactNL", "AvQuality", "SumContactNL.AvQuality")), 
            match(sample, c("Study 1", "Study 2", "Study 3", "RE")))

    alpha <- 0.05

  meta.parametric.plt.longdata2 <- meta.parametric.plt.longdata %>%
    mutate(
      index = as.integer(sapply(seq(from = 2, by=6, length.out = 3), seq, length.out=4)),
      vi = ((upr - lwr)/(2 * qnorm(alpha/2, lower.tail = FALSE)))^2,
      wi = 1/sqrt(vi),
      psize = wi/sum(wi, na.rm = TRUE),
      psize2 = (psize - min(psize, na.rm = TRUE))/(max(psize, na.rm = TRUE) - min(psize, na.rm = TRUE)),
      psize3 = (psize2 * 1) + 0.5
    )

  polyDat <- data.frame(
    y = c(
      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"],
      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"] - .25,
      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"],
      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"] + .25
    ),
    x = c(
      meta.parametric.plt.longdata2$lwr[meta.parametric.plt.longdata2$sample == "RE"],
      meta.parametric.plt.longdata2$beta[meta.parametric.plt.longdata2$sample == "RE"],
      meta.parametric.plt.longdata2$upr[meta.parametric.plt.longdata2$sample == "RE"],
      meta.parametric.plt.longdata2$beta[meta.parametric.plt.longdata2$sample == "RE"]
    ),
    lab = rep(paste("RE", 1:3), 4)
  )

  lab <- lapply(unique(meta.parametric.plt.longdata2$name), append, c(unique(meta.parametric.plt.longdata2$sample), "")) %>% unlist

  plot1 <- ggplot() +
    geom_point(
      data = meta.parametric.plt.longdata2[sample != "RE",],
      aes(y = index, x = beta),
      shape = 15,
      size = meta.parametric.plt.longdata2[sample != "RE", psize3] * 3
    ) +
    geom_errorbarh(data = meta.parametric.plt.longdata2[sample != "RE",],
                   aes(y = index, xmin = lwr, xmax = upr),
                   height = 0.25) +
    geom_polygon(data = polyDat, 
                 mapping = aes(x = x, y = y, group = lab)) +
    geom_vline(
      xintercept = 0,
      color = "black",
      linetype = "dashed",
      cex = 0.5,
      alpha = 1
    ) +
    scale_y_continuous(
      name = "",
      expand  = expansion(add = 1),
      breaks = seq(lab),
      labels = lab,
      trans = "reverse"
    ) +
    scale_x_continuous(
      limits = c(-1, 1),
      breaks = seq(-1, 1, 0.5),
      expand = c(0, 0)
    ) +
    xlab("Semi-Partial Correlation (95% CI)") +
    ggtitle("Predictors by Study") +
    theme_Publication() +
    theme(
      plot.title = element_text(hjust = 0, size=12, face = "bold"),
      plot.title.position = "plot",
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.text.y = element_text(size = 12, colour = "black", hjust=0, face = rep(c("bold", rep("plain", 5)),3)),
      axis.line.x = element_line(colour = "black"),
      axis.text.x.bottom = element_text(size = 12, colour = "black"),
      axis.title.x = element_text(size = 12, colour = "black")
    )

## Estiamte and CI table
  tab1 <- ggplot(meta.parametric.plt.longdata2, aes(y = lab)) +
    ylab(NULL) + xlab("  ") +
    labs(title = "space") +
    geom_text(aes(
      y = rev(index),
      x = 1,
      label = paste(sprintf("%0.2f", round(beta, digits = 2)), CI)
    ),
    size = 4,
    hjust = 1) + 
    scale_x_continuous(
      limits = c(-1, 1)
    ) +
    ggtitle("Estimate [95% CI]") +
    theme_Publication() +
    theme(
      plot.title = element_text(hjust = 1, size = 12),
      axis.line = element_blank(),
      axis.text.x = element_text(color = "white"),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.y = element_blank(),
      legend.position = "none",
      panel.background = element_blank(),
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.background = element_blank()
    )

grid.arrange(plot1, tab1, layout_matrix = matrix(c(1,1,1,2), nrow = 1))

png(file = "Figures/forestParametricGeneralLm.png", width = 700) 
  grid.arrange(plot1, tab1, layout_matrix = matrix(c(1,1,1,2), nrow = 1))
dev.off()

@@

```{generalForestPltComb}
effGeneral <- rbind(
  eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Aggregate Linear Regression",
           metaId = paste(coef, analysis, sep = ".")),
  GeneralLmerMeta$eff %>%
    mutate(analysis = "(B) Mixed Effects Regression",
           metaId = paste(coef, analysis, sep = "."))
)

metaSubForest(effGeneral, 
              title = "Meta Analysis: Forest Plot Contact Hypothesis \n[Parametric]",
              filename = "GeneralComb_WeirdScale",
              addAbove = 5,
              width = 600,
              height = 600)
```

@@

```{theoryForestPltComb}
effTheory <- rbind(
  TheoryMetaQualityNeed$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Quality ~ Core Need",
           metaId = paste(coef, analysis, sep = ".")),
  TheoryMetaAttitudeNeed$eff %>%
    mutate(analysis = "(B) Attitude ~ Core Need",
           metaId = paste(coef, analysis, sep = ".")),
  TheoryMetaAttitudeNeedQuality$eff %>%
    mutate(analysis = "(C) Attitude ~ Core Need + Quality",
           metaId = paste(coef, analysis, sep = "."))
)

metaSubForest(effTheory, 
              title = "Meta Analysis: Forest Plot Core Need Fulfillment \n[Parametric]",
              filename = "TheoryComb",
              addAbove = 0,
              width = 600,
              height = 600)
```

@@

```{robustForestPltComb}
effRobust <- rbind(
  robustMetaContact$eff %>%
    filter(coef != "(Intercept)") %>%
    mutate(analysis = "(A) Contact and Need Fulfillment",
           metaId = paste(coef, analysis, sep = ".")),
  robustMetaSDT$eff %>%
    mutate(analysis = "(B) Other Needs",
           metaId = paste(coef, analysis, sep = "."))
)

metaSubForest(effRobust, 
              title = "Meta Analysis: Forest Plot Robustness Analysis \n[Parametric]",
              filename = "RobustnessComb",
              addAbove = 17,
              width = 600,
              height = 800)
```
